---
title: "Uber data plots"
author: "Daniel Oyeleye"
date: "2023-10-24"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## R Markdown



```{r warning=FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
```

Returns a data frame with the variables total number of rides for each hour of the day, base and month
```{r}
rides_per_hour_base_month <- function(df){
  return (df %>% group_by(Hour, Base, Month)  %>% dplyr:: summarise(num_rides = n()))
}

```

```{r message=FALSE}
april_sep14 <- read.csv("C:\\Users\\danie\\Documents\\projects\\data projects\\uber data\\uber_april_sep14.csv")
rides_hbm <- rides_per_hour_base_month(april_sep14)
```

Scatter plot, box plot and histogram of number of rides per hour of day
```{r, echo=FALSE}
ggplot(data=rides_hbm) +
  geom_point(mapping = aes(x=Hour, y = num_rides))+ labs(title = "number of rides vs hour", y="number of rides")
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Hour)) + labs(y = "number of rides")
ggplot(data=rides_hbm) +
  geom_boxplot(mapping = aes(y=num_rides, color = Hour)) + labs(y = "number of rides")
```

Histogram, scatter plot and box plot of number of rides per base
```{r, echo=FALSE}
ggplot(data=rides_hbm) +
  geom_point(mapping = aes(x=Base, y = num_rides)) + labs(title = "number of rides vs base", y="number of rides")
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Base)) + labs(y = "number of rides")
ggplot(data=rides_hbm) +
  geom_boxplot(mapping = aes(y=num_rides, color=Base)) + labs(y = "number of rides")
```

Histogram, scatter plot and box plot of number of rides per month
```{r}
ggplot(data=rides_hbm) +
  geom_point(mapping = aes(x=Month, y = num_rides)) + labs(title = "number of rides vs month", y="number of rides")
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Month)) + labs(y = "number of rides")
ggplot(data=rides_hbm) +
  geom_boxplot(mapping = aes(y=num_rides, color=Month)) + labs(y = "number of rides")
```

Histogram of number of rides per base and month
```{r, echo=FALSE}
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Base, fill=Month)) + labs(y = "number of rides")
```

Histogram of number of rides per hour of day, base and month
```{r, echo=FALSE}
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Hour, color=Month, fill=Base)) + labs(y = "number of rides")
```

Histogram of number of rides per hour of day and base
```{r, echo=FALSE}
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Hour, fill=Base)) + labs(y = "number of rides")
```

Histogram of number of rides per hour of day and month
```{r, echo=FALSE}
ggplot(data=april_sep14) +
  geom_bar(mapping = aes(x=Hour, fill=Month)) + labs(y = "number of rides")
```

